\documentclass[a4paper,11pt]{article}
\usepackage[table]{xcolor}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{euscript}
\usepackage{boxedminipage}
\usepackage{lscape}
\usepackage{minitoc}
\usepackage{epsfig,psfrag,graphicx,verbatim}
\usepackage{natbib}
\usepackage{booktabs, longtable}
\usepackage{url}
\usepackage{makeidx}

%% Define a new 'code' style for the url package that will use a sans serif font.
\makeatletter
\def\url@codestyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\sffamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{code}

\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\textwidth}{16cm}
\setlength{\textheight}{23cm}
\title{ICEACE Reference Manual}
\author{Bulent Ozel - bulent.ozel@gmail.com}
\date{\today}

\makeindex

\begin{document}
\rowcolors[]{2}{lightgray!40}{yellow!25} %% color table rows with alternating colors
\maketitle
\newpage
\begin{abstract}
This documentation includes a reference manual for ICEACE Model. The documented model is implementation of a closed economy. The calibration of the closed economy is based on economic activities of Iceland.

This manual summarizes model parameters, agent types, their memory spaces and behaviours, messages within the communication mechanism and advanced data types developed for the model.
\end{abstract}

\newpage

\tableofcontents
\clearpage

\section{ICEACE FLAME Implementation}

\subsection{firm}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for firm agent.}}
\label{Table: firm Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{bank_id}} \index{\url{bank_id}} & \parbox{10cm}{Primary bank of a firm.} \\
\midrule
\parbox{5cm}{\url{int} \url{isconstructor}} \index{\url{isconstructor}} & \parbox{10cm}{Identifies if the firm is a constractor firm or not.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{The day of the month to act at production and labour.} \\
\midrule
\parbox{5cm}{\url{int} \url{isinsolvent}} \index{\url{isinsolvent}} & \parbox{10cm}{The variable indicates if the firm is a replacement of an insolvent producer.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_week_to_act}} \index{\url{day_of_week_to_act}} & \parbox{10cm}{Day of the week to act for consumption.} \\
\midrule
\parbox{5cm}{\url{double} \url{average_goods_price}} \index{\url{average_goods_price}} & \parbox{10cm}{Average goods price in the market.} \\
\midrule
\parbox{5cm}{\url{int_array} \url{employees}} \index{\url{employees}} & \parbox{10cm}{Holds employee ids} \\
\midrule
\parbox{5cm}{\url{int} \url{manager}} \index{\url{manager}} & \parbox{10cm}{Holds id of the manager.} \\
\midrule
\parbox{5cm}{\url{double} \url{wage_offer}} \index{\url{wage_offer}} & \parbox{10cm}{Monthly wage offer.} \\
\midrule
\parbox{5cm}{\url{double} \url{average_wage}} \index{\url{average_wage}} & \parbox{10cm}{Average wage in the market.} \\
\midrule
\parbox{5cm}{\url{int} \url{no_employees}} \index{\url{no_employees}} & \parbox{10cm}{Number of employees} \\
\midrule
\parbox{5cm}{\url{int} \url{vacancies}} \index{\url{vacancies}} & \parbox{10cm}{Number of vacancies} \\
\midrule
\parbox{5cm}{\url{int} \url{employees_needed}} \index{\url{employees_needed}} & \parbox{10cm}{Number of workers a firm needs for next production} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_wages_paid}} \index{\url{day_of_month_wages_paid}} & \parbox{10cm}{The day of the month wages paid.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_productivity}} \index{\url{labour_productivity}} & \parbox{10cm}{Productivity of a unit labour.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_productivity}} \index{\url{capital_productivity}} & \parbox{10cm}{Physical capital productivity.} \\
\midrule
\parbox{5cm}{\url{int} \url{capital_goods}} \index{\url{capital_goods}} & \parbox{10cm}{Physical capital owned by a firm in units.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_goods_price}} \index{\url{capital_goods_price}} & \parbox{10cm}{Unit price for capital goods.} \\
\midrule
\parbox{5cm}{\url{int} \url{production_current}} \index{\url{production_current}} & \parbox{10cm}{Total number of goods produced in current month.} \\
\midrule
\parbox{5cm}{\url{int} \url{expected_sales}} \index{\url{expected_sales}} & \parbox{10cm}{An estimate of production for incoming period.} \\
\midrule
\parbox{5cm}{\url{int} \url{production_plan}} \index{\url{production_plan}} & \parbox{10cm}{Production plan for next month.} \\
\midrule
\parbox{5cm}{\url{double} \url{unit_goods_price}} \index{\url{unit_goods_price}} & \parbox{10cm}{Price of a unit of goods produced by a firm.} \\
\midrule
\parbox{5cm}{\url{double} \url{unit_cost}} \index{\url{unit_cost}} & \parbox{10cm}{Unit production cost of a consumption good.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_production_completed}} \index{\url{day_of_month_production_completed}} & \parbox{10cm}{The day of the month amount of production is computed.} \\
\midrule
\parbox{5cm}{\url{double} \url{unit_house_price}} \index{\url{unit_house_price}} & \parbox{10cm}{Unit price of an house.} \\
\midrule
\parbox{5cm}{\url{int} \url{projects}} \index{\url{projects}} & \parbox{10cm}{Holds projects under construction. Indices denote number of months left for completion.} \\
\midrule
\parbox{5cm}{\url{double} \url{loans_interest_rate}} \index{\url{loans_interest_rate}} & \parbox{10cm}{Rate of interest paid by firms to banks for the loans.} \\
\midrule
\parbox{5cm}{\url{double} \url{debt}} \index{\url{debt}} & \parbox{10cm}{Total debt of the firm.} \\
\midrule
\parbox{5cm}{\url{int} \url{inventory}} \index{\url{inventory}} & \parbox{10cm}{Unsold inventory from previous month.} \\
\midrule
\parbox{5cm}{\url{int} \url{sales}} \index{\url{sales}} & \parbox{10cm}{Total number of sales within a month.} \\
\midrule
\parbox{5cm}{\url{double} \url{revenues}} \index{\url{revenues}} & \parbox{10cm}{Total revenue from sales. It is offset quarterly.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_assets}} \index{\url{total_assets}} & \parbox{10cm}{Total assets of a firm.} \\
\midrule
\parbox{5cm}{\url{double} \url{operating_costs}} \index{\url{operating_costs}} & \parbox{10cm}{Total operation costs.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_costs}} \index{\url{labour_costs}} & \parbox{10cm}{Total labour costs.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_interest_payments}} \index{\url{total_interest_payments}} & \parbox{10cm}{Total ineterests paid on a quarterly  basis for the bank loans.} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_paid}} \index{\url{dividends_paid}} & \parbox{10cm}{Amount of dividends paid to share holders via Equity Fund.} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_to_be_paid}} \index{\url{dividends_to_be_paid}} & \parbox{10cm}{Amount of dividends to be paid based on previous quarter operation.} \\
\midrule
\parbox{5cm}{\url{double} \url{retained_earnings}} \index{\url{retained_earnings}} & \parbox{10cm}{Amount of dividends retained by the firm.} \\
\midrule
\parbox{5cm}{\url{double} \url{net_earnings}} \index{\url{net_earnings}} & \parbox{10cm}{Quarterly profit after ineterest payments.} \\
\midrule
\parbox{5cm}{\url{double} \url{ebit}} \index{\url{ebit}} & \parbox{10cm}{Firm earnings before ineterest and taxes.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Firm equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Liquidity.} \\
\midrule
\parbox{5cm}{\url{int} \url{isliquidshort}} \index{\url{isliquidshort}} & \parbox{10cm}{The variable holds wheather a firm had any liquidity need in the latest quarter.} \\
\midrule
\parbox{5cm}{\url{int} \url{hasloan}} \index{\url{hasloan}} & \parbox{10cm}{The variable holds wheather a firm been credited by a bank for the loan that was requested.} \\
\midrule
\parbox{5cm}{\url{int} \url{hasinvestment}} \index{\url{hasinvestment}} & \parbox{10cm}{The variable holds wheather a firm has recieved investment from the fund for its liquidity need.} \\
\midrule
\parbox{5cm}{\url{int} \url{isilliquid}} \index{\url{isilliquid}} & \parbox{10cm}{Flag 0 or 1. Tells whether the firm ended up in illiquidity bankruptcy.} \\
\midrule
\parbox{5cm}{\url{double} \url{planned_investment_costs}} \index{\url{planned_investment_costs}} & \parbox{10cm}{Amount of investment to be made.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity_need}} \index{\url{liquidity_need}} & \parbox{10cm}{The variable holds wheather a firm needs liquidity to pay debt and dividends.} \\
\midrule
\parbox{5cm}{\url{loan} \url{loan_list}} \index{\url{loan_list}} & \parbox{10cm}{Holds loans owed to each bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_tax_rate}} \index{\url{labour_tax_rate}} & \parbox{10cm}{Tax rate to be used to pay labour tax.} \\
\midrule
\parbox{5cm}{\url{double} \url{delta_housing_price}} \index{\url{delta_housing_price}} & \parbox{10cm}{Monthly change on average housing prices.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for firm agent.}}
\label{Table: firm Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{firm_init_post_id}} \index{\url{firm_init_post_id}} & \parbox{10cm}{Firm posts its Id for employment initilialization.} \\
\midrule
\parbox{5cm}{\url{firm_init_employment}} \index{\url{firm_init_employment}} & \parbox{10cm}{Firm recieves its list of employees.} \\
\midrule
\parbox{5cm}{\url{firm_init_balancesheet}} \index{\url{firm_init_balancesheet}} & \parbox{10cm}{Synchronizing the mortgage debt and deposit with respective banks.} \\
\midrule
\parbox{5cm}{\url{firm_iterate}} \index{\url{firm_iterate}} & \parbox{10cm}{Resumes with its regular iteration loop.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Skip the bank account updates.} \\
\midrule
\parbox{5cm}{\url{firm_update_bank_account}} \index{\url{firm_update_bank_account}} & \parbox{10cm}{Deposits/updates its liquidity to bank.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Handles if the firm is not a regular firm.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Works when the firm is a constructor.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the week to sell.} \\
\midrule
\parbox{5cm}{\url{firm_consumption_supply}} \index{\url{firm_consumption_supply}} & \parbox{10cm}{A firm ships its goods to malls.} \\
\midrule
\parbox{5cm}{\url{firm_consumption_receive_sales}} \index{\url{firm_consumption_receive_sales}} & \parbox{10cm}{A firm recieves goods unsold and sales liquidity from the mall.} \\
\midrule
\parbox{5cm}{\url{firm_consumption_update_market_price}} \index{\url{firm_consumption_update_market_price}} & \parbox{10cm}{Firm checks goods prices.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Labour hiring is not active.} \\
\midrule
\parbox{5cm}{\url{firm_labour_workforce_needed}} \index{\url{firm_labour_workforce_needed}} & \parbox{10cm}{The firm computes required number of employees needed for incoming month.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Firm does nothing} \\
\midrule
\parbox{5cm}{\url{firm_labour_fire}} \index{\url{firm_labour_fire}} & \parbox{10cm}{The firm decides to fire if employee needed is below number of employees it does have.} \\
\midrule
\parbox{5cm}{\url{firm_labour_job_announcement_stage1}} \index{\url{firm_labour_job_announcement_stage1}} & \parbox{10cm}{The agent posts available positions.} \\
\midrule
\parbox{5cm}{\url{firm_labour_job_offer_stage1}} \index{\url{firm_labour_job_offer_stage1}} & \parbox{10cm}{The agent takes job matches done by jpoffice.} \\
\midrule
\parbox{5cm}{\url{firm_labour_update}} \index{\url{firm_labour_update}} & \parbox{10cm}{The agent updates labour status. In case of resignments.} \\
\midrule
\parbox{5cm}{\url{firm_labour_job_announcement_stage2}} \index{\url{firm_labour_job_announcement_stage2}} & \parbox{10cm}{The agent posts unfilled positions.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The agent has no vacant positions} \\
\midrule
\parbox{5cm}{\url{firm_labour_job_offer_stage2}} \index{\url{firm_labour_job_offer_stage2}} & \parbox{10cm}{The agent completes the job placement.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Does nothing at the point when it is not last day of the month.} \\
\midrule
\parbox{5cm}{\url{firm_labour_pay_wages}} \index{\url{firm_labour_pay_wages}} & \parbox{10cm}{Pay wages and update liquidity.} \\
\midrule
\parbox{5cm}{\url{firm_labour_trace_wages}} \index{\url{firm_labour_trace_wages}} & \parbox{10cm}{Firm checks wage in the market and updates its wage offer.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of month or the first day of the month.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The state serves to check the activity cases.} \\
\midrule
\parbox{5cm}{\url{firm_production_skip}} \index{\url{firm_production_skip}} & \parbox{10cm}{The firm is new entrant has initialized with an employee and an inventory.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The firm is a new entrant due to insolvency of inherited firm.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Sets a producer role.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Set the constructor role.} \\
\midrule
\parbox{5cm}{\url{firm_production_produce_goods}} \index{\url{firm_production_produce_goods}} & \parbox{10cm}{Firm audits number of items produced. Updates inventory accordingly.} \\
\midrule
\parbox{5cm}{\url{firm_production_set_price}} \index{\url{firm_production_set_price}} & \parbox{10cm}{Firm sets price of goods produced.} \\
\midrule
\parbox{5cm}{\url{firm_production_plan}} \index{\url{firm_production_plan}} & \parbox{10cm}{Firm determines number of items to be produced for the next period.} \\
\midrule
\parbox{5cm}{\url{firm_production_compute_labour_demand}} \index{\url{firm_production_compute_labour_demand}} & \parbox{10cm}{Firm determines required number of labourers for current production plan.} \\
\midrule
\parbox{5cm}{\url{firm_production_construct_houses}} \index{\url{firm_production_construct_houses}} & \parbox{10cm}{Firm releases number of items produced. Updates project status accordingly.} \\
\midrule
\parbox{5cm}{\url{firm_production_construction_plan}} \index{\url{firm_production_construction_plan}} & \parbox{10cm}{Firm sets the construction project plan.} \\
\midrule
\parbox{5cm}{\url{firm_production_construction_labour_demand}} \index{\url{firm_production_construction_labour_demand}} & \parbox{10cm}{Firm determines required number of labourers for current construction plan.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{firm_credit_compute_income_statement}} \index{\url{firm_credit_compute_income_statement}} & \parbox{10cm}{computing firm balance sheet.} \\
\midrule
\parbox{5cm}{\url{firm_credit_investment_decisions}} \index{\url{firm_credit_investment_decisions}} & \parbox{10cm}{computing firm balance sheet.} \\
\midrule
\parbox{5cm}{\url{firm_credit_compute_dividends}} \index{\url{firm_credit_compute_dividends}} & \parbox{10cm}{computing dividends to be paid.} \\
\midrule
\parbox{5cm}{\url{firm_credit_check_liquidity_need}} \index{\url{firm_credit_check_liquidity_need}} & \parbox{10cm}{Firm checks if it needs liquidity to pay loans and dividends.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Firm does not need loans.} \\
\midrule
\parbox{5cm}{\url{firm_credit_demand_loans_1}} \index{\url{firm_credit_demand_loans_1}} & \parbox{10cm}{Firm computes loan demand and places a demand if it needs and if it is allowed to do so.} \\
\midrule
\parbox{5cm}{\url{firm_credit_borrow_loans_1}} \index{\url{firm_credit_borrow_loans_1}} & \parbox{10cm}{Firm checks whether first loan request is accepted. When not, places another request to another bank.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The firm has gotten loan.} \\
\midrule
\parbox{5cm}{\url{firm_credit_borrow_loans_2}} \index{\url{firm_credit_borrow_loans_2}} & \parbox{10cm}{Firm checks weather second loan request is accepted.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The firm has gotten loan in the second trial.} \\
\midrule
\parbox{5cm}{\url{firm_credit_request_equityfund_investment}} \index{\url{firm_credit_request_equityfund_investment}} & \parbox{10cm}{The firm checks its illiquidity state. It places a request for investment from Equity Fund.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The firm checks for decision by Equity Fund.} \\
\midrule
\parbox{5cm}{\url{firm_credit_check_equityfund_investment}} \index{\url{firm_credit_check_equityfund_investment}} & \parbox{10cm}{The firm checks for decision by Equity Fund.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The firm has the investment goes paying loans.} \\
\midrule
\parbox{5cm}{\url{firm_credit_illiquidity_bankrupt}} \index{\url{firm_credit_illiquidity_bankrupt}} & \parbox{10cm}{Firm cannot recieve fund goes illiquidity.} \\
\midrule
\parbox{5cm}{\url{firm_credit_pay_interest_on_loans}} \index{\url{firm_credit_pay_interest_on_loans}} & \parbox{10cm}{Each quarter firm sends out intterest on the loans it has.} \\
\midrule
\parbox{5cm}{\url{firm_credit_pay_dividends}} \index{\url{firm_credit_pay_dividends}} & \parbox{10cm}{At the end of a quarter, a firm sends net profit to the equity fund.} \\
\midrule
\parbox{5cm}{\url{firm_credit_do_balance_sheet}} \index{\url{firm_credit_do_balance_sheet}} & \parbox{10cm}{Updating the balance sheet.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Firm is not insolvent. Keeps it regular activities.} \\
\midrule
\parbox{5cm}{\url{firm_credit_insolvency_bankruptcy}} \index{\url{firm_credit_insolvency_bankruptcy}} & \parbox{10cm}{The firm checks its illiquidity state, checking the deal with Equity Fund.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not time to act.} \\
\midrule
\parbox{5cm}{\url{firm_credit_check_interest_rate}} \index{\url{firm_credit_check_interest_rate}} & \parbox{10cm}{Firm checks quarterly interest rate.} \\
\midrule
\parbox{5cm}{\url{firm_credit_check_tax_rate}} \index{\url{firm_credit_check_tax_rate}} & \parbox{10cm}{Firm checks quarterly tax rate.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Handles if the firm is not a constructor.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Works when the firm is a constructor.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the first day of the month.} \\
\midrule
\parbox{5cm}{\url{firm_housing_enter_market}} \index{\url{firm_housing_enter_market}} & \parbox{10cm}{Firm goes to market when it has housing units to sell.} \\
\midrule
\parbox{5cm}{\url{firm_housing_collect_sale_revenues}} \index{\url{firm_housing_collect_sale_revenues}} & \parbox{10cm}{Firm collects sale revenues.} \\
\midrule
\parbox{5cm}{\url{firm_housing_update_market_price}} \index{\url{firm_housing_update_market_price}} & \parbox{10cm}{Firm checks housing prices.} \\
\end{longtable}

\subsection{household}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for household agent.}}
\label{Table: household Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{bank_id}} \index{\url{bank_id}} & \parbox{10cm}{The ID of the bank an household has. Household applies to her bank for mortgage and deposits.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_week_to_act}} \index{\url{day_of_week_to_act}} & \parbox{10cm}{Day of the week to act for consumption.} \\
\midrule
\parbox{5cm}{\url{double} \url{weekly_consumption_budget}} \index{\url{weekly_consumption_budget}} & \parbox{10cm}{Regualr weekly consumption budget computed for the quarter.} \\
\midrule
\parbox{5cm}{\url{double} \url{mall_budget}} \index{\url{mall_budget}} & \parbox{10cm}{Consumption budget that can be spent for the week.} \\
\midrule
\parbox{5cm}{\url{double} \url{quarterly_price_change}} \index{\url{quarterly_price_change}} & \parbox{10cm}{Quarterly price change of consumption goods.} \\
\midrule
\parbox{5cm}{\url{int} \url{my_employer_id}} \index{\url{my_employer_id}} & \parbox{10cm}{Employer ID of an household. A 0 means unemployed.} \\
\midrule
\parbox{5cm}{\url{double} \url{wage}} \index{\url{wage}} & \parbox{10cm}{Current wage earned.} \\
\midrule
\parbox{5cm}{\url{int} \url{ismanager}} \index{\url{ismanager}} & \parbox{10cm}{1 for the manegers, 0 for the regular workers.} \\
\midrule
\parbox{5cm}{\url{double} \url{government_benefits}} \index{\url{government_benefits}} & \parbox{10cm}{General benefit plus unemployment benefit recieved from the government.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{The day of the month to act for seeking a job.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_wage_recieved}} \index{\url{day_of_month_wage_recieved}} & \parbox{10cm}{The day of the month to wage recieved.} \\
\midrule
\parbox{5cm}{\url{double} \url{mortgages_interest_rate}} \index{\url{mortgages_interest_rate}} & \parbox{10cm}{Rate of interest set by the central bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_tax_rate}} \index{\url{labour_tax_rate}} & \parbox{10cm}{Rate of tax set by the government.} \\
\midrule
\parbox{5cm}{\url{mortgage_array} \url{mortgages_list}} \index{\url{mortgages_list}} & \parbox{10cm}{List of mortgages debted by households.} \\
\midrule
\parbox{5cm}{\url{double} \url{mortgages}} \index{\url{mortgages}} & \parbox{10cm}{Total mortgage.} \\
\midrule
\parbox{5cm}{\url{double} \url{housing_payment}} \index{\url{housing_payment}} & \parbox{10cm}{Holds total mortgage payment done within the last quarter.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Household equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{housing_price}} \index{\url{housing_price}} & \parbox{10cm}{Market value of a unit housing.} \\
\midrule
\parbox{5cm}{\url{int} \url{housing_units}} \index{\url{housing_units}} & \parbox{10cm}{Number of housing units owned by a household.} \\
\midrule
\parbox{5cm}{\url{int} \url{n_shares}} \index{\url{n_shares}} & \parbox{10cm}{Number of shares an household owns.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Liquidity.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_income}} \index{\url{capital_income}} & \parbox{10cm}{Equity fund shares recieved quarterly.} \\
\midrule
\parbox{5cm}{\url{double} \url{previous_wages}} \index{\url{previous_wages}} & \parbox{10cm}{Holds wages earned in three previous months.} \\
\midrule
\parbox{5cm}{\url{double} \url{previous_benefits}} \index{\url{previous_benefits}} & \parbox{10cm}{Holds benefits from the govenment in three previous months.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_income}} \index{\url{labour_income}} & \parbox{10cm}{Labour income for last 3 months.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_assets}} \index{\url{total_assets}} & \parbox{10cm}{Total assets owned by an household.} \\
\midrule
\parbox{5cm}{\url{double} \url{housing_value}} \index{\url{housing_value}} & \parbox{10cm}{Monetary value of housing units owned by an household.} \\
\midrule
\parbox{5cm}{\url{double} \url{expected_housing_payment}} \index{\url{expected_housing_payment}} & \parbox{10cm}{It keeps payment amount for the incoming quarter.} \\
\midrule
\parbox{5cm}{\url{int} \url{hmarket_role}} \index{\url{hmarket_role}} & \parbox{10cm}{The variable sets households market role.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity_ratio}} \index{\url{equity_ratio}} & \parbox{10cm}{Current equity ratio of an household} \\
\midrule
\parbox{5cm}{\url{double} \url{minimum_equity_ratio}} \index{\url{minimum_equity_ratio}} & \parbox{10cm}{Minimum equity ratio required for a household to apply for mortgage.} \\
\midrule
\parbox{5cm}{\url{double} \url{mortgage_costs}} \index{\url{mortgage_costs}} & \parbox{10cm}{Holds mortgage costs, principal plus ineterests paid for last three months.} \\
\midrule
\parbox{5cm}{\url{double} \url{delta_housing_value}} \index{\url{delta_housing_value}} & \parbox{10cm}{Value change on housing value on a monthly basis.} \\
\midrule
\parbox{5cm}{\url{int} \url{mortgage_choice}} \index{\url{mortgage_choice}} & \parbox{10cm}{Type of mortgage household chooses.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for household agent.}}
\label{Table: household Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{household_init_post_id}} \index{\url{household_init_post_id}} & \parbox{10cm}{Household posts its Id for employment initilialization.} \\
\midrule
\parbox{5cm}{\url{household_init_employment}} \index{\url{household_init_employment}} & \parbox{10cm}{Household recieves agent Id of his employer.} \\
\midrule
\parbox{5cm}{\url{household_init_balancesheet}} \index{\url{household_init_balancesheet}} & \parbox{10cm}{Synchronizing the mortgage debt and deposit with respective banks.} \\
\midrule
\parbox{5cm}{\url{household_iterate}} \index{\url{household_iterate}} & \parbox{10cm}{Resumes its regular iteration.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Skip the bank account updates.} \\
\midrule
\parbox{5cm}{\url{household_update_bank_account}} \index{\url{household_update_bank_account}} & \parbox{10cm}{Deposits/updates its liquidity to bank.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the first day of the month to compute monthly consumption.} \\
\midrule
\parbox{5cm}{\url{household_consumption_compute_budget}} \index{\url{household_consumption_compute_budget}} & \parbox{10cm}{It is the first day of the month, time to compute monthly consumption.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the week to shop.} \\
\midrule
\parbox{5cm}{\url{household_consumption_demand}} \index{\url{household_consumption_demand}} & \parbox{10cm}{A household demands a consumption amounted to the available budget he/she has.} \\
\midrule
\parbox{5cm}{\url{household_consumption_recieve_goods}} \index{\url{household_consumption_recieve_goods}} & \parbox{10cm}{A household recieves goods bought from the mall.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of month.} \\
\midrule
\parbox{5cm}{\url{household_consumption_trace_cpi}} \index{\url{household_consumption_trace_cpi}} & \parbox{10cm}{Household traces monthly cpi.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Job searching is not active.} \\
\midrule
\parbox{5cm}{\url{household_labour_check_fired}} \index{\url{household_labour_check_fired}} & \parbox{10cm}{Household checks layout status.} \\
\midrule
\parbox{5cm}{\url{household_labour_reemployment_application}} \index{\url{household_labour_reemployment_application}} & \parbox{10cm}{Stage 01 of job applications. Already employed households apply with a turnover probability} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Stage 01 of job applications. Unemployed households skip this stage} \\
\midrule
\parbox{5cm}{\url{household_labour_turnover}} \index{\url{household_labour_turnover}} & \parbox{10cm}{A job turnover.} \\
\midrule
\parbox{5cm}{\url{household_labour_employment_application}} \index{\url{household_labour_employment_application}} & \parbox{10cm}{Stage 02 of job market. Unemployed households apply.} \\
\midrule
\parbox{5cm}{\url{household_labour_employment}} \index{\url{household_labour_employment}} & \parbox{10cm}{A new employment.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Does nothing at the point when it is not last day of the month.} \\
\midrule
\parbox{5cm}{\url{household_labour_receive_wage}} \index{\url{household_labour_receive_wage}} & \parbox{10cm}{Receives payment and update wage history.} \\
\midrule
\parbox{5cm}{\url{household_labour_report_status}} \index{\url{household_labour_report_status}} & \parbox{10cm}{Sends out its employment status.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{The household does not own any shares of firms.} \\
\midrule
\parbox{5cm}{\url{household_credit_collect_shares}} \index{\url{household_credit_collect_shares}} & \parbox{10cm}{At the end of a quarter household recieves shares from the firms via Equity Fund.} \\
\midrule
\parbox{5cm}{\url{household_credit_do_balance_sheet}} \index{\url{household_credit_do_balance_sheet}} & \parbox{10cm}{Computing the balance sheet.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of the month.} \\
\midrule
\parbox{5cm}{\url{household_credit_collect_benefits}} \index{\url{household_credit_collect_benefits}} & \parbox{10cm}{Collect general transfer benefits and/or unemployment benefit from the government.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of a quarter.} \\
\midrule
\parbox{5cm}{\url{household_credit_check_interest_rate}} \index{\url{household_credit_check_interest_rate}} & \parbox{10cm}{Households check the interest rate which is set by CB.} \\
\midrule
\parbox{5cm}{\url{household_credit_update_mortgage_rates}} \index{\url{household_credit_update_mortgage_rates}} & \parbox{10cm}{Households updates annuity, principal and interest payment amounts.} \\
\midrule
\parbox{5cm}{\url{household_credit_check_tax_rate}} \index{\url{household_credit_check_tax_rate}} & \parbox{10cm}{Households check the tax rate which is set by government.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the first day of the month.} \\
\midrule
\parbox{5cm}{\url{household_housing_market_role}} \index{\url{household_housing_market_role}} & \parbox{10cm}{Sets the households market role in real estate for the current month.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Household is not active at the market.} \\
\midrule
\parbox{5cm}{\url{household_housing_check_wealth}} \index{\url{household_housing_check_wealth}} & \parbox{10cm}{Households attempts to the market with regular buyer role.} \\
\midrule
\parbox{5cm}{\url{household_housing_sell}} \index{\url{household_housing_sell}} & \parbox{10cm}{Households enters the market with regular seller role.} \\
\midrule
\parbox{5cm}{\url{household_housing_fire_sell}} \index{\url{household_housing_fire_sell}} & \parbox{10cm}{Household enters the market with a fire seller role.} \\
\midrule
\parbox{5cm}{\url{household_housing_collect_sale_revenue}} \index{\url{household_housing_collect_sale_revenue}} & \parbox{10cm}{Household collects sale revenue and if he is a fire seller pays mortgage with it.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Household does not have enough equity to buy.} \\
\midrule
\parbox{5cm}{\url{household_housing_enter_market}} \index{\url{household_housing_enter_market}} & \parbox{10cm}{Household goes to the market.} \\
\midrule
\parbox{5cm}{\url{household_housing_buy}} \index{\url{household_housing_buy}} & \parbox{10cm}{Household updates her assets based on the result he gets from housing market.} \\
\midrule
\parbox{5cm}{\url{household_housing_update_market_price}} \index{\url{household_housing_update_market_price}} & \parbox{10cm}{Household checks new avg housing market price.} \\
\midrule
\parbox{5cm}{\url{household_housing_pay_mortgages}} \index{\url{household_housing_pay_mortgages}} & \parbox{10cm}{Household sends out mortgage payments.} \\
\midrule
\parbox{5cm}{\url{household_housing_debt_writeoff}} \index{\url{household_housing_debt_writeoff}} & \parbox{10cm}{When debt of household drops below a certain threshold its earnings, the debt is written off.} \\
\end{longtable}

\subsection{equityfund}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for equityfund agent.}}
\label{Table: equityfund Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{Activation day for the shareholder audition.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_wages_paid}} \index{\url{day_of_month_wages_paid}} & \parbox{10cm}{Activation day for the shareholder audition.} \\
\midrule
\parbox{5cm}{\url{double} \url{share_firms}} \index{\url{share_firms}} & \parbox{10cm}{Shares owned by regular firms.} \\
\midrule
\parbox{5cm}{\url{double} \url{share_construction_firms}} \index{\url{share_construction_firms}} & \parbox{10cm}{Shares owned by constructor firms.} \\
\midrule
\parbox{5cm}{\url{double} \url{share_banks}} \index{\url{share_banks}} & \parbox{10cm}{Shares owned by banks.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Firm equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Liquidity.} \\
\midrule
\parbox{5cm}{\url{int} \url{n_shares}} \index{\url{n_shares}} & \parbox{10cm}{Number of households(shares) to recieve liquid shares from firm net income.} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_recieved}} \index{\url{dividends_recieved}} & \parbox{10cm}{Total amount dividends recieved from firms and banks} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_retained}} \index{\url{dividends_retained}} & \parbox{10cm}{Total amount of dividends retained.} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_paid}} \index{\url{dividends_paid}} & \parbox{10cm}{Total amount of dividends distributed to shareholders.} \\
\midrule
\parbox{5cm}{\url{double} \url{firm_investment}} \index{\url{firm_investment}} & \parbox{10cm}{Total amount of liquidity used for firms with liquidity needs.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_tax_rate}} \index{\url{capital_tax_rate}} & \parbox{10cm}{Tax rate used at determining amount of tax on dividends.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for equityfund agent.}}
\label{Table: equityfund Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{equityfund_init}} \index{\url{equityfund_init}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{equityfund_iterate}} \index{\url{equityfund_iterate}} & \parbox{10cm}{Notifies its id.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a month.} \\
\midrule
\parbox{5cm}{\url{equityfund_audit_dividends}} \index{\url{equityfund_audit_dividends}} & \parbox{10cm}{Makes a sensus on size of dividends.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_invest_illiquids}} \index{\url{equityfund_credit_invest_illiquids}} & \parbox{10cm}{The equity fund invests certain firms to resolve their liquidity problem.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_collect_bank_shares}} \index{\url{equityfund_credit_collect_bank_shares}} & \parbox{10cm}{At the end of a quarter collect net income from the banks in the market.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_collect_firm_shares}} \index{\url{equityfund_credit_collect_firm_shares}} & \parbox{10cm}{At the end of a quarter collect net income from the firms in the market.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_distribute_shares}} \index{\url{equityfund_credit_distribute_shares}} & \parbox{10cm}{At the end of a quarter net income per household is distributed.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of a quarter.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_compute_income_statement}} \index{\url{equityfund_credit_compute_income_statement}} & \parbox{10cm}{Equity Fund computes the income statement.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_do_balance_sheet}} \index{\url{equityfund_credit_do_balance_sheet}} & \parbox{10cm}{Equity fund balance sheet accounting activities.} \\
\midrule
\parbox{5cm}{\url{equityfund_credit_check_tax_rate}} \index{\url{equityfund_credit_check_tax_rate}} & \parbox{10cm}{Equity fund checks quarterly tax rate.} \\
\end{longtable}

\subsection{bank}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for bank agent.}}
\label{Table: bank Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{Activation day.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_week_to_act}} \index{\url{day_of_week_to_act}} & \parbox{10cm}{Day of the week to act.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_assets}} \index{\url{total_assets}} & \parbox{10cm}{Total assets of the banks.} \\
\midrule
\parbox{5cm}{\url{double} \url{loans}} \index{\url{loans}} & \parbox{10cm}{Loans to firms.} \\
\midrule
\parbox{5cm}{\url{double} \url{loans_start}} \index{\url{loans_start}} & \parbox{10cm}{Loans to firms at the start of the quarter.} \\
\midrule
\parbox{5cm}{\url{double} \url{mortgages}} \index{\url{mortgages}} & \parbox{10cm}{Mortgages to households.} \\
\midrule
\parbox{5cm}{\url{double} \url{deposits}} \index{\url{deposits}} & \parbox{10cm}{Deposits recieved from private sector.} \\
\midrule
\parbox{5cm}{\url{double} \url{centralbank_debt}} \index{\url{centralbank_debt}} & \parbox{10cm}{Debt to central bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Firm equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Liquidity.} \\
\midrule
\parbox{5cm}{\url{double} \url{revenues}} \index{\url{revenues}} & \parbox{10cm}{Revenues of the bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_writeoffs}} \index{\url{total_writeoffs}} & \parbox{10cm}{Total of writeoff loss a bank has.} \\
\midrule
\parbox{5cm}{\url{double} \url{interest_rate}} \index{\url{interest_rate}} & \parbox{10cm}{Rate of interest set by central bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{interests_accrued}} \index{\url{interests_accrued}} & \parbox{10cm}{Total interest a bank has collected from loans and mortgages.} \\
\midrule
\parbox{5cm}{\url{double} \url{interests_paid}} \index{\url{interests_paid}} & \parbox{10cm}{Total interest a bank has paid to for its central bank debts.} \\
\midrule
\parbox{5cm}{\url{double} \url{dividends_paid}} \index{\url{dividends_paid}} & \parbox{10cm}{Amount of dividends paid to share holders via Equity Fund.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_dividends}} \index{\url{total_dividends}} & \parbox{10cm}{Amount of dividends banks have to distribute.} \\
\midrule
\parbox{5cm}{\url{double} \url{retained_earnings}} \index{\url{retained_earnings}} & \parbox{10cm}{Retained earnings in the case of capital inadequecy.} \\
\midrule
\parbox{5cm}{\url{double} \url{net_earnings}} \index{\url{net_earnings}} & \parbox{10cm}{Earnings from interests minus costs.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_costs}} \index{\url{total_costs}} & \parbox{10cm}{Total costs of banks. It is interest paid to CB and writeoffs recieved.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for bank agent.}}
\label{Table: bank Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{bank_init_loans}} \index{\url{bank_init_loans}} & \parbox{10cm}{Gathers loans from firms.} \\
\midrule
\parbox{5cm}{\url{bank_init_mortgages}} \index{\url{bank_init_mortgages}} & \parbox{10cm}{Gather mortgages from households.} \\
\midrule
\parbox{5cm}{\url{bank_init_deposits}} \index{\url{bank_init_deposits}} & \parbox{10cm}{Gather deposits from firms and households.} \\
\midrule
\parbox{5cm}{\url{bank_init_balancesheet}} \index{\url{bank_init_balancesheet}} & \parbox{10cm}{Bank initializes total assets, equity, debt to central bank and liquidity.} \\
\midrule
\parbox{5cm}{\url{bank_iterate}} \index{\url{bank_iterate}} & \parbox{10cm}{Bank resumes its iterative functions.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Skip the bank account updates.} \\
\midrule
\parbox{5cm}{\url{bank_update_deposits}} \index{\url{bank_update_deposits}} & \parbox{10cm}{Deposits/updates its liquidity to bank.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{bank_credit_compute_income_statement}} \index{\url{bank_credit_compute_income_statement}} & \parbox{10cm}{Bank computes income statement.} \\
\midrule
\parbox{5cm}{\url{bank_credit_compute_dividends}} \index{\url{bank_credit_compute_dividends}} & \parbox{10cm}{Bank evaluates loan requests firstly. } \\
\midrule
\parbox{5cm}{\url{bank_credit_do_balance_sheet}} \index{\url{bank_credit_do_balance_sheet}} & \parbox{10cm}{Bank balance sheet accounting activities.} \\
\midrule
\parbox{5cm}{\url{bank_credit_process_loan_requests_1}} \index{\url{bank_credit_process_loan_requests_1}} & \parbox{10cm}{Bank evaluates first loan requests.} \\
\midrule
\parbox{5cm}{\url{bank_credit_process_loan_requests_2}} \index{\url{bank_credit_process_loan_requests_2}} & \parbox{10cm}{Bank evaluates first loan requests.} \\
\midrule
\parbox{5cm}{\url{bank_credit_recieve_loan_writeoffs}} \index{\url{bank_credit_recieve_loan_writeoffs}} & \parbox{10cm}{Bank updates its loss.} \\
\midrule
\parbox{5cm}{\url{bank_credit_recieve_new_entrant_loan_requests}} \index{\url{bank_credit_recieve_new_entrant_loan_requests}} & \parbox{10cm}{Bank recieve request for new entrant requests.} \\
\midrule
\parbox{5cm}{\url{bank_credit_collect_loan_interests}} \index{\url{bank_credit_collect_loan_interests}} & \parbox{10cm}{Bank evaluates first loan requests.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not time to act.} \\
\midrule
\parbox{5cm}{\url{bank_credit_check_interest_rate}} \index{\url{bank_credit_check_interest_rate}} & \parbox{10cm}{Bank checks centralbank ineterest rate.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the first day of the month.} \\
\midrule
\parbox{5cm}{\url{bank_housing_compute_capital_status}} \index{\url{bank_housing_compute_capital_status}} & \parbox{10cm}{Bank computes its crediting status.} \\
\midrule
\parbox{5cm}{\url{bank_housing_deliver_mortages}} \index{\url{bank_housing_deliver_mortages}} & \parbox{10cm}{Bank collects mortage requests from real estate agency.} \\
\midrule
\parbox{5cm}{\url{bank_housing_recieve_mortgage_principals}} \index{\url{bank_housing_recieve_mortgage_principals}} & \parbox{10cm}{Bank collects mortage debt principal payments from households.} \\
\midrule
\parbox{5cm}{\url{bank_housing_recieve_mortgages}} \index{\url{bank_housing_recieve_mortgages}} & \parbox{10cm}{Bank collects regular mortgage payments from households.} \\
\midrule
\parbox{5cm}{\url{bank_housing_debt_writeoff}} \index{\url{bank_housing_debt_writeoff}} & \parbox{10cm}{Bank recieves mortgage written off.} \\
\end{longtable}

\subsection{government}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for government agent.}}
\label{Table: government Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{double} \url{average_wage}} \index{\url{average_wage}} & \parbox{10cm}{Average wage for employed households.} \\
\midrule
\parbox{5cm}{\url{double} \url{unemployment_rate}} \index{\url{unemployment_rate}} & \parbox{10cm}{The unemployment rate} \\
\midrule
\parbox{5cm}{\url{int} \url{population_size}} \index{\url{population_size}} & \parbox{10cm}{Number of households.} \\
\midrule
\parbox{5cm}{\url{double} \url{debt}} \index{\url{debt}} & \parbox{10cm}{Debt to central bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Government equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Government liquidity.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{Day of the month to act.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_wages_paid}} \index{\url{day_of_month_wages_paid}} & \parbox{10cm}{The day of month wages paid. It is the end of month.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_tax_rate}} \index{\url{capital_tax_rate}} & \parbox{10cm}{Government rate on capital income.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_tax_rate}} \index{\url{labour_tax_rate}} & \parbox{10cm}{Government rate on labour income.} \\
\midrule
\parbox{5cm}{\url{double} \url{labour_tax_income}} \index{\url{labour_tax_income}} & \parbox{10cm}{Collected amount of labour tax.} \\
\midrule
\parbox{5cm}{\url{double} \url{capital_tax_income}} \index{\url{capital_tax_income}} & \parbox{10cm}{Collected amount of capital tax.} \\
\midrule
\parbox{5cm}{\url{double} \url{gov_general_benefit_rate}} \index{\url{gov_general_benefit_rate}} & \parbox{10cm}{Rate of general benefits to distribute to all housholds.} \\
\midrule
\parbox{5cm}{\url{double} \url{gov_unemployment_rate}} \index{\url{gov_unemployment_rate}} & \parbox{10cm}{Rate of unemployment benefit with respect to average wage.} \\
\midrule
\parbox{5cm}{\url{double} \url{general_benefits}} \index{\url{general_benefits}} & \parbox{10cm}{Amount of general benefits distributed to households.} \\
\midrule
\parbox{5cm}{\url{double} \url{unemployment_benefits}} \index{\url{unemployment_benefits}} & \parbox{10cm}{Amount of unemployment benefits distributed by the government.} \\
\midrule
\parbox{5cm}{\url{double} \url{earnings}} \index{\url{earnings}} & \parbox{10cm}{Government earnings from taxes.} \\
\midrule
\parbox{5cm}{\url{double} \url{centralbank_income}} \index{\url{centralbank_income}} & \parbox{10cm}{Quarterly collected amount of profits from centralbank.} \\
\midrule
\parbox{5cm}{\url{double} \url{expenditures}} \index{\url{expenditures}} & \parbox{10cm}{Government expenditures on unemployment and general benefit payments.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for government agent.}}
\label{Table: government Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{government_init}} \index{\url{government_init}} & \parbox{10cm}{Agent runtime initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{government_iterate}} \index{\url{government_iterate}} & \parbox{10cm}{Regular loop start point.} \\
\midrule
\parbox{5cm}{\url{government_trace_unemployment_status}} \index{\url{government_trace_unemployment_status}} & \parbox{10cm}{Makes a sensus on employment status.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the start of a quarter.} \\
\midrule
\parbox{5cm}{\url{government_collect_capital_tax}} \index{\url{government_collect_capital_tax}} & \parbox{10cm}{It is the start of the quarter.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of a month.} \\
\midrule
\parbox{5cm}{\url{government_distribute_general_benefits}} \index{\url{government_distribute_general_benefits}} & \parbox{10cm}{It distributes general benefits.} \\
\midrule
\parbox{5cm}{\url{government_distribute_unemployment_benefits}} \index{\url{government_distribute_unemployment_benefits}} & \parbox{10cm}{It distributes unemployment benefits.} \\
\midrule
\parbox{5cm}{\url{government_collect_labour_tax}} \index{\url{government_collect_labour_tax}} & \parbox{10cm}{Labour tax is collected} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of a quarter.} \\
\midrule
\parbox{5cm}{\url{government_collect_centralbank_profit}} \index{\url{government_collect_centralbank_profit}} & \parbox{10cm}{The government collects net profit from the centralbank.} \\
\midrule
\parbox{5cm}{\url{government_compute_income_statement}} \index{\url{government_compute_income_statement}} & \parbox{10cm}{Government computes its income statement.} \\
\midrule
\parbox{5cm}{\url{government_do_balance_sheet}} \index{\url{government_do_balance_sheet}} & \parbox{10cm}{Government balance sheet accounting activities.} \\
\midrule
\parbox{5cm}{\url{government_update_fiscal_policy}} \index{\url{government_update_fiscal_policy}} & \parbox{10cm}{Government sets tax rate, general benefits and unemployment benefits} \\
\end{longtable}

\subsection{centralbank}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for centralbank agent.}}
\label{Table: centralbank Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{Day of the month to act.} \\
\midrule
\parbox{5cm}{\url{double} \url{unemployment_rate}} \index{\url{unemployment_rate}} & \parbox{10cm}{Unemployment rate. It is updated monthly.} \\
\midrule
\parbox{5cm}{\url{double} \url{inflation_rate}} \index{\url{inflation_rate}} & \parbox{10cm}{inflation rate. It is updated quarterly.} \\
\midrule
\parbox{5cm}{\url{double} \url{consumption_goods_prices}} \index{\url{consumption_goods_prices}} & \parbox{10cm}{Unemployment rate. It is updated monthly} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_week_to_act}} \index{\url{day_of_week_to_act}} & \parbox{10cm}{Day of the week to act.} \\
\midrule
\parbox{5cm}{\url{transaction} \url{goods}} \index{\url{goods}} & \parbox{10cm}{Weakly transaction summary at the market.} \\
\midrule
\parbox{5cm}{\url{double} \url{weekly_price_averages}} \index{\url{weekly_price_averages}} & \parbox{10cm}{Weakly price averages at the market.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_wages_paid}} \index{\url{day_of_month_wages_paid}} & \parbox{10cm}{The day of the month wages paid.} \\
\midrule
\parbox{5cm}{\url{double} \url{interest_rate}} \index{\url{interest_rate}} & \parbox{10cm}{Rate of interest set by central bank.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity}} \index{\url{liquidity}} & \parbox{10cm}{Central Bank liquidity} \\
\midrule
\parbox{5cm}{\url{double} \url{loans_banks}} \index{\url{loans_banks}} & \parbox{10cm}{loans to firms.} \\
\midrule
\parbox{5cm}{\url{double} \url{loans_government}} \index{\url{loans_government}} & \parbox{10cm}{loans to the government.} \\
\midrule
\parbox{5cm}{\url{double} \url{fiat_money}} \index{\url{fiat_money}} & \parbox{10cm}{Outstanding fiat money.} \\
\midrule
\parbox{5cm}{\url{double} \url{equity}} \index{\url{equity}} & \parbox{10cm}{Firm equity.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity_banks}} \index{\url{liquidity_banks}} & \parbox{10cm}{Liquidity kept for banks.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity_government}} \index{\url{liquidity_government}} & \parbox{10cm}{Liquidity kept for the government.} \\
\midrule
\parbox{5cm}{\url{double} \url{liquidity_equityfund}} \index{\url{liquidity_equityfund}} & \parbox{10cm}{Liquidity kept for the fund.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_assets}} \index{\url{total_assets}} & \parbox{10cm}{Central Bank total assets.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_writeoffs}} \index{\url{total_writeoffs}} & \parbox{10cm}{Central Bank loss due to bank bailouts.} \\
\midrule
\parbox{5cm}{\url{double} \url{interests_accrued}} \index{\url{interests_accrued}} & \parbox{10cm}{Amount of interest collected from banks and government.} \\
\midrule
\parbox{5cm}{\url{double} \url{revenues}} \index{\url{revenues}} & \parbox{10cm}{Central Bank revenues.} \\
\midrule
\parbox{5cm}{\url{double} \url{net_earnings}} \index{\url{net_earnings}} & \parbox{10cm}{Central Bank net earnings.} \\
\midrule
\parbox{5cm}{\url{double} \url{total_costs}} \index{\url{total_costs}} & \parbox{10cm}{Central Bank total costs.} \\
\midrule
\parbox{5cm}{\url{transaction} \url{houses}} \index{\url{houses}} & \parbox{10cm}{Monthly transaction summary at the market.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for centralbank agent.}}
\label{Table: centralbank Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{centralbank_init_balancesheet}} \index{\url{centralbank_init_balancesheet}} & \parbox{10cm}{Synchronizing the bank debts.} \\
\midrule
\parbox{5cm}{\url{centralbank_iterate}} \index{\url{centralbank_iterate}} & \parbox{10cm}{Resumes its regular iteration.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the week to act.} \\
\midrule
\parbox{5cm}{\url{centralbank_trace_goods_prices}} \index{\url{centralbank_trace_goods_prices}} & \parbox{10cm}{It is the day of the week to act.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of month.} \\
\midrule
\parbox{5cm}{\url{centralbank_update_price_indices}} \index{\url{centralbank_update_price_indices}} & \parbox{10cm}{The central bank computes monthly price average.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the month to act.} \\
\midrule
\parbox{5cm}{\url{centralbank_trace_unemployment_status}} \index{\url{centralbank_trace_unemployment_status}} & \parbox{10cm}{Makes a sensus on employment status.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not time to act.} \\
\midrule
\parbox{5cm}{\url{centralbank_collect_interest_payments}} \index{\url{centralbank_collect_interest_payments}} & \parbox{10cm}{Central Bank collects interest payments from banks.} \\
\midrule
\parbox{5cm}{\url{centralbank_process_debt_requests}} \index{\url{centralbank_process_debt_requests}} & \parbox{10cm}{Central Bank receives new debt requests from banks and collects debt payments from banks.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not time to act.} \\
\midrule
\parbox{5cm}{\url{centralbank_compute_income_statement}} \index{\url{centralbank_compute_income_statement}} & \parbox{10cm}{Central Bank computes income statement.} \\
\midrule
\parbox{5cm}{\url{centralbank_process_government_requests}} \index{\url{centralbank_process_government_requests}} & \parbox{10cm}{Central Bank processes loan requests and loan payments from the government.} \\
\midrule
\parbox{5cm}{\url{centralbank_do_balance_sheet}} \index{\url{centralbank_do_balance_sheet}} & \parbox{10cm}{Central Bank balance sheet accounting activities.} \\
\midrule
\parbox{5cm}{\url{centralbank_set_interest_rate}} \index{\url{centralbank_set_interest_rate}} & \parbox{10cm}{Central bank sets the interest rate.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the month to act.} \\
\midrule
\parbox{5cm}{\url{centralbank_trace_housing_prices}} \index{\url{centralbank_trace_housing_prices}} & \parbox{10cm}{It is the day of the month to act.} \\
\end{longtable}

\subsection{jpoffice}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for jpoffice agent.}}
\label{Table: jpoffice Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{The day of mont to perform job matching.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for jpoffice agent.}}
\label{Table: jpoffice Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Agent initilialization.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Proceeding with regular agent loop.} \\
\midrule
\parbox{5cm}{\url{jpoffice_init_employment}} \index{\url{jpoffice_init_employment}} & \parbox{10cm}{Job placement office collects household and firm ids and forms network of initial employment.} \\
\midrule
\parbox{5cm}{\url{jpoffice_iterate}} \index{\url{jpoffice_iterate}} & \parbox{10cm}{Notifies its id.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{Job matching is not active.} \\
\midrule
\parbox{5cm}{\url{jpoffice_labour_stage1}} \index{\url{jpoffice_labour_stage1}} & \parbox{10cm}{Collecting vacancies and job applications. Vacancies and turnover applications are matched.} \\
\midrule
\parbox{5cm}{\url{jpoffice_labour_stage2}} \index{\url{jpoffice_labour_stage2}} & \parbox{10cm}{Second stage job matching.} \\
\end{longtable}

\subsection{mall}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for mall agent.}}
\label{Table: mall Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_week_to_act}} \index{\url{day_of_week_to_act}} & \parbox{10cm}{Day of the week to act for consumption.} \\
\midrule
\parbox{5cm}{\url{transaction} \url{goods_transactions}} \index{\url{goods_transactions}} & \parbox{10cm}{Weakly transaction summary at the market.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for mall agent.}}
\label{Table: mall Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{mall_init}} \index{\url{mall_init}} & \parbox{10cm}{Notifies its id.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the day of the week to shop.} \\
\midrule
\parbox{5cm}{\url{mall_consumption_shopping}} \index{\url{mall_consumption_shopping}} & \parbox{10cm}{Mall collecting supplies from the firms, demands from the households.} \\
\midrule
\parbox{5cm}{\url{mall_consumption_summary}} \index{\url{mall_consumption_summary}} & \parbox{10cm}{The agent reports summary of transactions.} \\
\end{longtable}

\subsection{reagency}

\begin{longtable}[H!]{ll}
\caption{{\bfseries List of memory variables for reagency agent.}}
\label{Table: reagency Memory}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{int} \url{id}} \index{\url{id}} & \parbox{10cm}{Agent ID.} \\
\midrule
\parbox{5cm}{\url{int} \url{day_of_month_to_act}} \index{\url{day_of_month_to_act}} & \parbox{10cm}{Activation day.} \\
\midrule
\parbox{5cm}{\url{int} \url{it_no}} \index{\url{it_no}} & \parbox{10cm}{Current iteration. Incremented daily bais.} \\
\midrule
\parbox{5cm}{\url{double} \url{mortgages_interest_rate}} \index{\url{mortgages_interest_rate}} & \parbox{10cm}{Rate of interest set by central bank.} \\
\midrule
\parbox{5cm}{\url{transaction} \url{housing_transactions}} \index{\url{housing_transactions}} & \parbox{10cm}{Monthly transaction summary at the market.} \\
\end{longtable}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of functions for reagency agent.}}
\label{Table: reagency Functions}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\midrule
\parbox{5cm}{\url{reagency_init}} \index{\url{reagency_init}} & \parbox{10cm}{Notifies its id.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the end of a quarter.} \\
\midrule
\parbox{5cm}{\url{reagency_check_interest_rate}} \index{\url{reagency_check_interest_rate}} & \parbox{10cm}{It checks interest rate.} \\
\midrule
\parbox{5cm}{\url{idle}} \index{\url{idle}} & \parbox{10cm}{It is not the first day of the month.} \\
\midrule
\parbox{5cm}{\url{reagency_housing_process}} \index{\url{reagency_housing_process}} & \parbox{10cm}{The agent collects requests and does the matchings.} \\
\midrule
\parbox{5cm}{\url{reagency_housing_summary}} \index{\url{reagency_housing_summary}} & \parbox{10cm}{The agent reports summary of transactions.} \\
\end{longtable}
\subsection{Messages}
See Table \ref{Table: Messages}.\begin{longtable}[H!]{ll}
\caption{{\bfseries List of messages.}}
\label{Table: Messages}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\url{firm_bank_init_loans} & \parbox{10cm}{Firm sends out its initialized loan info to bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank from which initial loan has gotten. }\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of loan.}\\
\midrule
\url{firm_bank_init_deposit} & \parbox{10cm}{Firm sends out its liquid money to bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank where liquid money to be deposited.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{firm_bank_update_deposit} & \parbox{10cm}{Firm sends out its liquid money to bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank where liquid money to be deposited.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{household_bank_init_mortgages} & \parbox{10cm}{Household sends out its initialized amount of mortgage info to its bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank from which initial mortgage has been acquired.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of mortgage.}\\
\midrule
\url{household_bank_init_deposit} & \parbox{10cm}{Household sends out its liquid money to bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank where liquid money to be deposited.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{household_bank_update_deposit} & \parbox{10cm}{Household sends out its liquid money to bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank where liquid money to be deposited.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{bank_centralbank_init_debt} & \parbox{10cm}{Bank informs its centralbank debt for initilialization.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The deptor bank id.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of debt.}\\
\midrule
\url{bank_centralbank_init_deposit} & \parbox{10cm}{Bank sends out its liquid money to centralbank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The depositor bank id.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{bank_centralbank_update_deposit} & \parbox{10cm}{Bank sends out its liquid money to centralbank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The depositor bank id.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{fund_centralbank_init_deposit} & \parbox{10cm}{Fund sends out its liquid money to centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{fund_centralbank_update_deposit} & \parbox{10cm}{Fund sends out its liquid money to centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{gov_centralbank_init_deposit} & \parbox{10cm}{Government sends out its liquid money to centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{gov_centralbank_update_deposit} & \parbox{10cm}{Government sends out its liquid money to centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquid money to be deposited.}\\
\midrule
\url{interest_rate} & \parbox{10cm}{The interest rate sent by the central bank.}\\
    \url{double} \url{rate} \index{\url{rate}} & \parbox{10cm}{The rate.}\\
\midrule
\url{capital_tax_rate} & \parbox{10cm}{Government tax rate on capital income.}\\
    \url{double} \url{value} \index{\url{value}} & \parbox{10cm}{Rate of the tax.}\\
\midrule
\url{labour_tax_rate} & \parbox{10cm}{Government tax rate on labour income.}\\
    \url{double} \url{value} \index{\url{value}} & \parbox{10cm}{Rate of the tax.}\\
\midrule
\url{household_jpoffice_id} & \parbox{10cm}{Household notifies his/her id.}\\
    \url{int} \url{household_id} \index{\url{household_id}} & \parbox{10cm}{The agent id.}\\
\midrule
\url{jpoffice_household_employer} & \parbox{10cm}{Firm notifies its id.}\\
    \url{int} \url{household_id} \index{\url{household_id}} & \parbox{10cm}{The agent id.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{The agent id.}\\
    \url{int} \url{position} \index{\url{position}} & \parbox{10cm}{The position. 1 for managers 0 for regulars.}\\
\midrule
\url{firm_jpoffice_id} & \parbox{10cm}{Firm notifies its id.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The agent id.}\\
    \url{int} \url{isconstructor} \index{\url{isconstructor}} & \parbox{10cm}{Firm type.}\\
\midrule
\url{jpoffice_firm_employee} & \parbox{10cm}{Firm notifies its id.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The agent id.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{The agent id.}\\
    \url{int} \url{position} \index{\url{position}} & \parbox{10cm}{The position. 1 for managers 0 for regulars.}\\
\midrule
\url{buy} & \parbox{10cm}{Weekly household consumption information.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Household agent ID.}\\
    \url{double} \url{budget} \index{\url{budget}} & \parbox{10cm}{Amount of liquid money to spend.}\\
\midrule
\url{bought} & \parbox{10cm}{Consumption summary.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Household agent ID.}\\
    \url{double} \url{money_spent} \index{\url{money_spent}} & \parbox{10cm}{Amount of liquid money that was spent.}\\
    \url{int} \url{received_quantity} \index{\url{received_quantity}} & \parbox{10cm}{Number of goods bought.}\\
\midrule
\url{sell} & \parbox{10cm}{Information on items to be sold at the mall.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Firm agent ID.}\\
    \url{double} \url{price} \index{\url{price}} & \parbox{10cm}{Unit price of goods to be sold.}\\
    \url{int} \url{inventory} \index{\url{inventory}} & \parbox{10cm}{Number of items to be sold.}\\
\midrule
\url{sold} & \parbox{10cm}{Sales summary.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Firm agent ID.}\\
    \url{int} \url{sold_quantities} \index{\url{sold_quantities}} & \parbox{10cm}{Number of sold quantities.}\\
\midrule
\url{goods_transactions_summary} & \parbox{10cm}{Weakly sent out transaction summary.}\\
    \url{int} \url{quantity} \index{\url{quantity}} & \parbox{10cm}{Number of goods sold out.}\\
    \url{double} \url{avg_price} \index{\url{avg_price}} & \parbox{10cm}{Weakly avg price.}\\
\midrule
\url{centralbank_households_quarterly_cpi} & \parbox{10cm}{Quarterly price change of consumption goods.}\\
    \url{double} \url{change} \index{\url{change}} & \parbox{10cm}{Quarterly price change of consumption goods.}\\
\midrule
\url{fired} & \parbox{10cm}{Sent by a firm to notify an employee who is fired.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Employee ID who has been fired.}\\
\midrule
\url{vacancy_stage1} & \parbox{10cm}{Sent by a Firm to post a vacancy.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{Firm agent ID who posts a new position.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Amount of salary to be offered.}\\
\midrule
\url{job_application_stage2} & \parbox{10cm}{Sent by an household to apply a posted vacancy.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Household agent ID who seeks employment.}\\
\midrule
\url{job_application_stage1} & \parbox{10cm}{Sent by an household to notifie jpoffice}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Household agent ID who applies for a new job.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Current amount of wage earned by the applicant.}\\
\midrule
\url{job_match_stage1} & \parbox{10cm}{Sent by a firm informing a filled position.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{Firm agent ID that has filled a post.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Household agent ID who has been offered a position.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Amount of salary that is offered.}\\
\midrule
\url{job_change} & \parbox{10cm}{Sent by a worker to notify a resigned position.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{Firm agent ID of the position held.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Household aent ID who is changing the job.}\\
\midrule
\url{vacancy_stage2} & \parbox{10cm}{Sent by a Firm to post unfilled vacancy.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{Firm agent ID who posts unfilled position.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Amount of salary to be offered.}\\
\midrule
\url{job_match_stage2} & \parbox{10cm}{Sent by a firm informing a filled position.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{Firm agent ID that has filled a post.}\\
    \url{int} \url{employee_id} \index{\url{employee_id}} & \parbox{10cm}{Household agent ID who has been offered a position.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Amount of salary that is offered.}\\
\midrule
\url{employment_status} & \parbox{10cm}{Sent by a household to report his/her employment status.}\\
    \url{int} \url{employer_id} \index{\url{employer_id}} & \parbox{10cm}{The employer. O stands for unemployed case.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Current wage of an household.}\\
    \url{int} \url{nshares} \index{\url{nshares}} & \parbox{10cm}{Number of shares one own.}\\
\midrule
\url{firm_household_wage_payment} & \parbox{10cm}{Posted by the firm agent.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm id.}\\
    \url{double} \url{wage} \index{\url{wage}} & \parbox{10cm}{Current wage offer by the firm.}\\
\midrule
\url{firm_bank_loan_request_1} & \parbox{10cm}{The loan requested by a firm.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{firm_bank_loan_request_2} & \parbox{10cm}{The loan requested by a firm.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{bank_firm_loan_acknowledge_1} & \parbox{10cm}{The loan that is acknowledged by a firms's own bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{bank_firm_loan_acknowledge_2} & \parbox{10cm}{The loan acknowledged for a firm by the other bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{bank_centralbank_debt_request} & \parbox{10cm}{Debt request by bank from the central bank.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank id}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{amount requested}\\
\midrule
\url{household_share} & \parbox{10cm}{Shares are sent to households.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Share per household.}\\
\midrule
\url{capital_tax} & \parbox{10cm}{Tax on capital earnings of households.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Total capital tax sent by household.}\\
\midrule
\url{labour_tax} & \parbox{10cm}{Tax on wage earning of households.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Total wage taxes sent to government by househols.}\\
\midrule
\url{unemployment_benefit} & \parbox{10cm}{Total unemployment benefit sent to households.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{}\\
\midrule
\url{general_benefit} & \parbox{10cm}{general benefit sent to households.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{}\\
\midrule
\url{fund_request} & \parbox{10cm}{Amount of the liquidity requested from Equity Fund.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{}\\
\midrule
\url{fund_request_ack} & \parbox{10cm}{Amount of the liquidity requested is confirmed by Equity Fund.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{}\\
\midrule
\url{new_entrant_loan} & \parbox{10cm}{The loan requested by the new entrant, that replaces the insolvent one.}\\
    \url{int} \url{firm_id} \index{\url{firm_id}} & \parbox{10cm}{The firm.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{firm_bank_interest_on_loan} & \parbox{10cm}{Quarterly interest that is paid by a firm.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{The bank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{The amount.}\\
\midrule
\url{loan_writeoff} & \parbox{10cm}{Amount of loan of a firm that is written off.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank to receive.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{}\\
\midrule
\url{firm_bank_insolvent_account} & \parbox{10cm}{Acount maintainance in case of insolvency.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Bank ID of the account.}\\
    \url{double} \url{liquidity} \index{\url{liquidity}} & \parbox{10cm}{Amount of liquidity}\\
\midrule
\url{firm_net_profit} & \parbox{10cm}{Net income send to Equity Fund.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Firm agent ID.}\\
    \url{int} \url{isconstructor} \index{\url{isconstructor}} & \parbox{10cm}{Flag to label whether the income is recieved from a constructor firm.}\\
    \url{double} \url{net_income} \index{\url{net_income}} & \parbox{10cm}{Net income to be distributed.}\\
\midrule
\url{bank_net_profit} & \parbox{10cm}{Net income send to Equity Fund.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Bank Agent ID.}\\
    \url{double} \url{net_income} \index{\url{net_income}} & \parbox{10cm}{Net income to be distributed.}\\
\midrule
\url{bank_centralbank_interest_payment} & \parbox{10cm}{Interest paid by bank to centralbank.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Bank Agent ID.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of interest payment.}\\
\midrule
\url{bank_centralbank_debt_payment} & \parbox{10cm}{Debt paid by bank to centralbank.}\\
    \url{int} \url{id} \index{\url{id}} & \parbox{10cm}{Bank Agent ID.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of debt paid back.}\\
\midrule
\url{gov_centralbank_debt_request} & \parbox{10cm}{Government requests debt from the centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of liquidity needed.}\\
\midrule
\url{gov_centralbank_debt_payment} & \parbox{10cm}{Government pays debt to centralbank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of payment.}\\
\midrule
\url{centralbank_government_profit} & \parbox{10cm}{Amount of profit transfered to the government. }\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of debt paid back.}\\
\midrule
\url{housing_price} & \parbox{10cm}{Sent real estate agency at the end of market.}\\
    \url{double} \url{price} \index{\url{price}} & \parbox{10cm}{Average unit price of housing for the month.}\\
\midrule
\url{buy_housing} & \parbox{10cm}{Sent by a household.}\\
    \url{int} \url{buyer_id} \index{\url{buyer_id}} & \parbox{10cm}{Household ID, the buyer.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Bank ID of the buyer. Used in case mortgage is needed.}\\
    \url{double} \url{liquidity} \index{\url{liquidity}} & \parbox{10cm}{Amount of liquidity an household have at the time to buy housing.}\\
    \url{double} \url{quarterly_income} \index{\url{quarterly_income}} & \parbox{10cm}{Quarterly net income, labour and capital, an household makes.}\\
    \url{double} \url{quarterly_mortgage_paid} \index{\url{quarterly_mortgage_paid}} & \parbox{10cm}{Quarterly mortgage payments being done by an household.}\\
    \url{int} \url{mortgage_choice} \index{\url{mortgage_choice}} & \parbox{10cm}{Mortgage choice of households while joining to housing market as a buyer.}\\
\midrule
\url{sell_housing} & \parbox{10cm}{Sent either by a constructor firm or an household.}\\
    \url{int} \url{seller_id} \index{\url{seller_id}} & \parbox{10cm}{Agent ID of the seller.}\\
    \url{double} \url{price} \index{\url{price}} & \parbox{10cm}{Unit price of housing.}\\
    \url{int} \url{quantity} \index{\url{quantity}} & \parbox{10cm}{Quantity of housing units to sell. Households are allowed to sell maximum of 1 unit.}\\
    \url{int} \url{type} \index{\url{type}} & \parbox{10cm}{Seller Roles: 1 fire seller; 2 regular seller; 0 firm seller.}\\
\midrule
\url{bought_housing} & \parbox{10cm}{Sent to an household.}\\
    \url{int} \url{buyer_id} \index{\url{buyer_id}} & \parbox{10cm}{Agent ID of the household who has bought one unit of housing.}\\
    \url{double} \url{liquidity_spent} \index{\url{liquidity_spent}} & \parbox{10cm}{Amount of liquid money used to buy a unit of housing.}\\
    \url{double} \url{mortgage_used} \index{\url{mortgage_used}} & \parbox{10cm}{Amount of mortgage used from the bank.}\\
    \url{double} \url{annuity} \index{\url{annuity}} & \parbox{10cm}{Annuity of the housing unit bought.}\\
\midrule
\url{sold_housing} & \parbox{10cm}{Sent either to a constructor firm or to an household.}\\
    \url{int} \url{seller_id} \index{\url{seller_id}} & \parbox{10cm}{Agent ID of the seller.}\\
    \url{int} \url{quantity_sold} \index{\url{quantity_sold}} & \parbox{10cm}{Quantity of housing units that has been sold.}\\
    \url{double} \url{price_sold} \index{\url{price_sold}} & \parbox{10cm}{Unit price of each sale.}\\
\midrule
\url{bank_reagency_credibility} & \parbox{10cm}{Posted by a bank. It shows total amount of mortgage a bank can provide for the market.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank.}\\
    \url{double} \url{equity} \index{\url{equity}} & \parbox{10cm}{Equity owned by bank.}\\
    \url{double} \url{risky_assets} \index{\url{risky_assets}} & \parbox{10cm}{Amount of risky assets owned by the bank.}\\
\midrule
\url{mortgage_requests} & \parbox{10cm}{Posted by a bank. It shows total amount of mortgage a bank can provide for the market.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of mortgage given out by the bank.}\\
\midrule
\url{mortgage_payment_from_sale} & \parbox{10cm}{Amount of mortgage principal mortgage paid by a household to a bank after a fire sale.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank to receive.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of mortgage paid to a bank by an household.}\\
\midrule
\url{mortgage_payment} & \parbox{10cm}{Regular mortage payments.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank to receive.}\\
    \url{double} \url{interest} \index{\url{interest}} & \parbox{10cm}{Amount of mortgage interest.}\\
    \url{double} \url{principal} \index{\url{principal}} & \parbox{10cm}{Amount of mortgage principal.}\\
\midrule
\url{mortgage_writeoff} & \parbox{10cm}{Amount of mortgage of a household that is written off.}\\
    \url{int} \url{bank_id} \index{\url{bank_id}} & \parbox{10cm}{Agent ID of the bank to receive.}\\
    \url{double} \url{amount} \index{\url{amount}} & \parbox{10cm}{Amount of mortgage interest.}\\
\midrule
\url{housing_transactions_summary} & \parbox{10cm}{Monthly transaction summary.}\\
    \url{int} \url{quantity} \index{\url{quantity}} & \parbox{10cm}{Number of housing units sold out.}\\
    \url{double} \url{avg_price} \index{\url{avg_price}} & \parbox{10cm}{Monthly avg price..}\\
\end{longtable}
\subsection{Constants}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of constants.}}
\label{Table: constants}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\url{int} \url{resume_mode} \index{\url{resume_mode}} & \parbox{10cm}{Flag, 0 or 1.  To re-start a simulation from a snapshot , it needs to be set to 1.}\\
\url{int} \url{print_debug_mode} \index{\url{print_debug_mode}} & \parbox{10cm}{Flag, 0 or 1.  To record simulation process stages and selected states for debugging purposes, it needs to be set to 1.}\\
\url{int} \url{warning_mode} \index{\url{warning_mode}} & \parbox{10cm}{Flag, 0 or 1.  To record unexpected states, this needs to be set to 1.}\\
\url{int} \url{data_collection_mode} \index{\url{data_collection_mode}} & \parbox{10cm}{Flag, 0 or 1. To record simulation data, it needs to be set to 1.}\\
\url{int} \url{collect_household_data} \index{\url{collect_household_data}} & \parbox{10cm}{Flag, 0 or 1. To record household simulation data, it needs to be set to 1.}\\
\url{int} \url{collect_firm_data} \index{\url{collect_firm_data}} & \parbox{10cm}{Flag, 0 or 1. To record firm simulation data, it needs to be set to 1.}\\
\url{double} \url{ratio_liquidity} \index{\url{ratio_liquidity}} & \parbox{10cm}{Ratio of liquidity to monthly disposable income.}\\
\url{double} \url{consumption_adjustment_speed} \index{\url{consumption_adjustment_speed}} & \parbox{10cm}{The consumption adjustment speed.}\\
\url{double} \url{wealth_effect} \index{\url{wealth_effect}} & \parbox{10cm}{A rate of influence from housing market to regular economy. Used by Household agents.}\\
\url{double} \url{turnover_probability} \index{\url{turnover_probability}} & \parbox{10cm}{A probability of a uniform distribution that determines turnover rate.}\\
\url{double} \url{production_markup} \index{\url{production_markup}} & \parbox{10cm}{Rate of increase in production by firms.}\\
\url{double} \url{price_markup} \index{\url{price_markup}} & \parbox{10cm}{Rate of increase set by firms on prices.}\\
\url{double} \url{firm_memory_persistance} \index{\url{firm_memory_persistance}} & \parbox{10cm}{A parameter holding to what extend firms previous sale history play on final production decision.}\\
\url{double} \url{ratio_fiscal_policy} \index{\url{ratio_fiscal_policy}} & \parbox{10cm}{Ratio of tax vs benefits to balance government deficit.}\\
\url{double} \url{ratio_capitalist_households} \index{\url{ratio_capitalist_households}} & \parbox{10cm}{It is the rate of households owning firm shares.}\\
\url{double} \url{inflation_target} \index{\url{inflation_target}} & \parbox{10cm}{It is used by central bank to compute monthly inflation.}\\
\url{double} \url{firms_minimum_equity_ratio} \index{\url{firms_minimum_equity_ratio}} & \parbox{10cm}{The paramter is used by funding agency to check equity requirement to invest in a firm.}\\
\url{double} \url{firm_startup_leverage} \index{\url{firm_startup_leverage}} & \parbox{10cm}{Firms' starting leverage'.}\\
\url{double} \url{household_startup_leverage} \index{\url{household_startup_leverage}} & \parbox{10cm}{Households' starting leverage'.}\\
\url{double} \url{car_buffer_threshold} \index{\url{car_buffer_threshold}} & \parbox{10cm}{Allowable ratio of risky assets owned by bank for crediting.}\\
\url{double} \url{housing_market_entrance_prob} \index{\url{housing_market_entrance_prob}} & \parbox{10cm}{Entrance probability of an household agent. It determines the chance for an household to be active at housing market.}\\
\url{double} \url{fire_sale_threshold} \index{\url{fire_sale_threshold}} & \parbox{10cm}{The ratio of debt payments to income, which is inspected at a fire sale decision.}\\
\url{double} \url{household_budget_constraint} \index{\url{household_budget_constraint}} & \parbox{10cm}{Budget constraint applied by banks for the mortgage applications.}\\
\url{double} \url{capital_adequecy_ratio} \index{\url{capital_adequecy_ratio}} & \parbox{10cm}{Allowable ratio of risky assets owned by bank for crediting.}\\
\url{double} \url{housing_price_up_rate} \index{\url{housing_price_up_rate}} & \parbox{10cm}{Allowable percentage increase in housing price.}\\
\url{double} \url{housing_price_down_rate} \index{\url{housing_price_down_rate}} & \parbox{10cm}{Allowable percentage decrease on a fire sale case by an household.}\\
\url{double} \url{household_mortgage_writeoff_high} \index{\url{household_mortgage_writeoff_high}} & \parbox{10cm}{Household budget threshold for mortgage write-off}\\
\url{double} \url{household_mortgage_writeoff_low} \index{\url{household_mortgage_writeoff_low}} & \parbox{10cm}{Household budget ratio for mortgage write-off}\\
\end{longtable}
\subsection{Datatypes}
\begin{longtable}[H!]{ll}
\caption{{\bfseries List of attributes for ADTs.}}
\label{Table: datatypes}\\
\toprule 
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endfirsthead
\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\bfseries Name & \bfseries Description \\ \hline 
\midrule
\endhead
\multicolumn{2}{r}{{\emph{Continued on next page}}} \\
\endfoot
\bottomrule
\endlastfoot
\url{transaction} \index{\url{transaction}} & \parbox{10cm}{A generic transaction data structure.} \\
    \url{int} \url{quantity} & \parbox{8cm}{Number of items within a period.}\\
    \url{double} \url{avg_price} & \parbox{8cm}{Average price on overall transactions.}\\
\midrule
\url{buyer} \index{\url{buyer}} & \parbox{10cm}{Consumer data.} \\
    \url{int} \url{id} & \parbox{8cm}{Id of the household agent.}\\
    \url{double} \url{budget} & \parbox{8cm}{Consumption budget to go.}\\
\midrule
\url{seller} \index{\url{seller}} & \parbox{10cm}{Seller data.} \\
    \url{int} \url{id} & \parbox{8cm}{Id of the firm agent.}\\
    \url{double} \url{price} & \parbox{8cm}{Unit price of goods to be sold.}\\
    \url{int} \url{inventory} & \parbox{8cm}{Number of items available for sale.}\\
    \url{double} \url{inv_price} & \parbox{8cm}{Inverse of price. It is used to decrease computation time at the mall.}\\
\midrule
\url{vacancy} \index{\url{vacancy}} & \parbox{10cm}{Firm vacancy information.} \\
    \url{int} \url{id} & \parbox{8cm}{Id of the firm agent.}\\
    \url{double} \url{wage} & \parbox{8cm}{Wage offered by the firm that holds the vacancy.}\\
\midrule
\url{employee} \index{\url{employee}} & \parbox{10cm}{Job applicant data.} \\
    \url{int} \url{id} & \parbox{8cm}{Id of the household agent.}\\
    \url{double} \url{wage} & \parbox{8cm}{Current wage of the job applicant.}\\
\midrule
\url{mortgage} \index{\url{mortgage}} & \parbox{10cm}{Household mortgage information.} \\
    \url{int} \url{bank_id} & \parbox{8cm}{Id of the bank from which mortgage is acquired.}\\
    \url{double} \url{principal} & \parbox{8cm}{Principal amount left}\\
    \url{int} \url{quarters_left} & \parbox{8cm}{Number of quarters left for the mortgage.}\\
    \url{double} \url{quarterly_interest} & \parbox{8cm}{Amount of interest to be paid within the current quarter.}\\
    \url{double} \url{quarterly_principal} & \parbox{8cm}{Amount of principal to be paid within the current quarter.}\\
    \url{double} \url{interestrate} & \parbox{8cm}{Interest rate of the mortgage.}\\
    \url{int} \url{mtype} & \parbox{8cm}{Type of mortgage.}\\
\midrule
\url{loan} \index{\url{loan}} & \parbox{10cm}{Used by firm to hold loans they owe to each bank.} \\
    \url{int} \url{bank_id} & \parbox{8cm}{Id of the bank from which loan is acquired.}\\
    \url{double} \url{amount} & \parbox{8cm}{The amount requested so far.}\\
    \url{double} \url{to_be_paid} & \parbox{8cm}{The amount to be paid.}\\
\midrule
\url{hbuyer} \index{\url{hbuyer}} & \parbox{10cm}{Buyer data at housing market.} \\
    \url{int} \url{buyer_id} & \parbox{8cm}{Household ID, the buyer.}\\
    \url{int} \url{bank_id} & \parbox{8cm}{Bank ID of the buyer. Used in case mortgage is needed.}\\
    \url{double} \url{liquidity} & \parbox{8cm}{Amount of liquidity an household have at the time to buy housing.}\\
    \url{double} \url{quarterly_income} & \parbox{8cm}{Quarterly net income, labour and capital, an household makes.}\\
    \url{double} \url{quarterly_mortgage_paid} & \parbox{8cm}{Quarterly mortgage payments being done by an household.}\\
    \url{int} \url{choice} & \parbox{8cm}{Mortgage choice of households while joining to housing market as a buyer.}\\
\midrule
\url{hseller} \index{\url{hseller}} & \parbox{10cm}{Seller data at housing market. Sent either by a constructor firm or an household.} \\
    \url{int} \url{seller_id} & \parbox{8cm}{Agent ID of the seller.}\\
    \url{double} \url{price} & \parbox{8cm}{Unit price of housing.}\\
    \url{int} \url{quantity} & \parbox{8cm}{Quantity of housing units to sell. Households are allowed to sell maximum of 1 unit.}\\
    \url{int} \url{type} & \parbox{8cm}{Seller Roles: 1 fire seller; 2 regular seller; 0 firm seller.}\\
\midrule
\url{hbank} \index{\url{hbank}} & \parbox{10cm}{Mortgaging data regarding the banks at the housing market.} \\
    \url{int} \url{id} & \parbox{8cm}{Agent ID of the bank.}\\
    \url{double} \url{equity} & \parbox{8cm}{Equity owned by bank.}\\
    \url{double} \url{risky_assets} & \parbox{8cm}{Amount of risky assets owned by the bank.}\\
    \url{double} \url{amount_mortgaged} & \parbox{8cm}{Amount of mortgage given out by the bank.}\\
\end{longtable}

\printindex

\end{document}
